---
title: "linear model from Web"
author: "Karen Gomez"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction

We predict a simulated strength score based on arm and grip strength. We will find 3 models and compare them. The response variable is numerical, and the explanatory variable is numerical, so we use the num~num helper file. 


## Model 1 SIM~ARMS

## Results
### graphical results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

This graph shows that as arm strength increases the simulation score does too. 

### numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation coefficient is 0.69 which shows that arm strength is related to sim score

### inferential results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

We have evidence that the intercept and the coefficient of arm are significantly different from 0. Therefore we reject the null hypothesis, due to the small p-value.


### prediction interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIM score. 


## Model 2 SIM~GRIP

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='red')
```

This graph shows that as grip strength increases, the simulation score does too. The spread of the points around the regression line, in the grip plot, is more than the model 1 strength plot. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation coefficient is 0.64 which shows that grip strength is related to sim score. The grip correlation coefficient is smaller than model 1's, 0.69.

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

We have evidence that the intercept and the coefficient of grip are significantly different from 0. Therefore we reject the null hypothesis due to the small p-value. 

#### predict model.2 at target point

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```

The prediction interval is from -3.1 to 2.0 for SIM score. 
  
## Model 3 SIM~ARM+GRIP

### Numerical Results

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation is 0.73, which shows that arm/grip strength is related to sims score.

### Inferential  (Build 2-dimentional model.3)

````{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```  

These coefficients are significant from 0 because the p-value is small, thus rejecting the null hypothesis. As arm goes up, sims will also go up because the coefficient is positive

### Prediction Interval

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.3, newdata, interval="predict")
```

The prediction interval is from 0.15 to -

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.3,model.1)
```

The p-value is .00000499 so I reject the null hypothesis. Model three is better than model one because the rss is smaller. 

### Model.2 vs Model.3

```{r}
anova(model.3,model.2)
```

Model three is better than model two because it has a smaller rss.

## Informally compare Model.1 with model.2

```{r}
anova(model.2,model.1)
```

Model one is better than model two because the rss for model one is smaller.

# Discussion and Conclusion

We tried fitting three models to the data and we found that each of the models were significant in terms of being able to predict the simulated strength score but when we looked at the analysis variance we found that model with ARM + GRIP was the best since it has a smaller RSS than all the others. 
